---
title: "farsfunction"
author: "Sanjaya J Shetty"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{farsfunction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The functions in the package will be using data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes

To install package use devtools package and download the package from Github repo

```{r, eval=FALSE}
devtools::install_github('SanjayShetty01/farsfunctions')
```

## Load the package

```{r setup, message=FALSE}
library(farsfunctions)
library(dplyr)
```


## Load the Dataset
```{r, warning=FALSE}
data = system.file('extdata', "accident_2013.csv.bz2", package = 'farsfunctions')

accidentData = fars_read(data)
```

the function `make_filename` lets you create a filename to load  the data

```{r}
make_filename(2013)
```

getting months and years info.
```{r}
accidentDataForNyears = fars_read_years(c(2013,2014))

head(accidentDataForNyears[[1]])
```

getting the summary of data for counting the number of accident
```{r, warning=FALSE, eval=FALSE}
year = 2013
fars_summarize_years(year)


```

Visualsing the place where the accident occurred. 
```{r, warning=FALSE,eval=FALSE}
state = 1
year = 2013
fars_map_state(state, year)
```
